Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-28 ms.tex
fixed bandpass correction equation
starting re-write of bandpass correction discussion

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. We 
have therefore computed dimensionless finite bandpass correction factors to 
account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
function of frequency:

@@

\begin{equation} \label{equ:bpcorr}
b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
adopted the DIRBE transmission curve.

>>>>

\subsection{Color Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
$\nu$. In practice, however, we wish to constrain our model using measurements 
in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
The \PLANCK~data products quote flux density per solid angle in MJy/sr under 
the `IRAS convention'. More precisely, each value reported in the \PLANCK~maps 
gives the amplitude of a power-law spectrum with $\alpha$=$-1$, evaluated at 
the nominal band center frequency, such that this spectrum integrated against 
the transmission reproduces the bolometer-measured power. Because our model 
spectra do not conform to the $\alpha$=$-1$ convention, we have computed color 
correction factors to account for the MBB($T$, $\beta$) spectral shape and the 
transmission as a function of frequency:

@@

\begin{equation} \label{equ:bpcorr}
b_{\nu_i}(T, \beta) = \frac{\int \nu^{\beta}B_{\nu}(T)\mathcal{T}_{\nu_i}(\nu) d\nu \bigg[\int (\nu_{i,c}/\nu)\mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
adopted the DIRBE transmission curve. These bandpass correction factors 
are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ 
is a prediction suitable for comparison to the \PLANCK~data products.
